%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/minhhoangbui/}{\Large Minh-Hoang Bui}} & Email : \href{mailto:minhhoangbui.vn@gmail.com}{minhhoangbui.vn@gmail.com}\\
  \href{https://minhhoangbui.github.io/}{https://minhhoangbui.github.io/} & Mobile : +84-070-488-6700 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Technology of Troyes}{Champagne-Ardenne, France}
      {Master of Science in Optimization and System Security}{Aug. 2016 -- Oct. 2017}
    \resumeSubheading
      {Ho Chi Minh University of Technology}{Ho Chi Minh City, Vietnam}
      {Bachelor of Engineering in Electrical and Electronics;  GPA: 8.29/10 }{Aug. 2012 -- July. 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Chappiebot Inc.}{Ho Chi Minh City, Vietnam}
      {Data Scientist}{Oct 2017 - Present}
      \resumeItemListStart
        \resumeItem{Computer Vision}
          {Research and implement state-of-the-art deep learning architectures for the task of image classification(ResNet, DenseNet...) and image similarity (Deep Ranking) in order to enhance user experience in an e-commerce site.}
        \resumeItem{Natural Language Processing (NLP)}
          {Develop a pool of algorithms to solve multiple problems in NLP like Text Classification, Name-Entity Recognition, etc. Various architectures are implemented: ConvNet, Attention Bi-LSTM, CRF etc. These techniques are used to develop a Personalized News Distribution platform for 24h Inc.}
        \resumeItem{Distributed Training}
          {Research Horovod(Uber), Apache Hadoop, Apache Spark for distributed model training when dealing with Big Data.}
        \resumeItem{Amazon Web Service}
          {Responsible for data organization with Amazon S3, algorithm dockerizing with Amazon ECS, cloud training and deployment with Amazon SageMake.}
        \resumeItem{Engineering Blog}
          {In charge of deep learning and mathematical-related content for the engineering blog of the company.}
      \resumeItemListEnd

    \resumeSubheading
      {CEA-LETI}{Campus MINATEC, Grenoble, France}
      {Engineering Intern}{Jan 2017 - Sep 2017}
      \resumeItemListStart
        \resumeItem{Edge Detection}
          {Understand the general concept of edge detection and some important gradient-based methods like Sobel-filter and Canny method with the help of OpenCV}
        \resumeItem{Active Contour}
          {Apprehend the mathematical complication of the method Active Contour which will be applied to SEM images in micro-technologies}
        \resumeItem{Optimization}
          {Understand various optimization techniques(CG, Powell, BFGS, Newton-based methods etc.) and their pros/cons with the help of Scipy}
        \resumeItem{Neural Network}
          {Work with another intern to compare the effectiveness of Neural Network method and Active Contour in contour detection with SEM images}
        \resumeItem{Code Organization}
          {Get familiar with version-control systems like SVN and Git}
      \resumeItemListEnd

    \resumeSubheading
      {Sirinhorn International Institute of Technology}{Pathum Thani, Thailand}
      {Research Intern}{06/2016- 08/2016}
      \resumeItemListStart
        \resumeItem{3D Reconstruction}
          {Get familiar with 3D Reconstruction mechanism and the definition of reversed engineering}
        \resumeItem{Image Processing}
          {Get familiar with various techniques in Image Processing like Hough Transform, Canny Detector with OpenCV}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{OtoNhanh.vn}
      {An e-commerce website which uses machine learning to simplify the car purchasing procedure in Vietnam}
    \resumeSubItem{Personalized News Distribution}
      {An application which recommends news and articles to user based on the user's insight with the help of machine learning}
    \resumeSubItem{Contour Detector with SEM image}
      {Building a algorithm which can detect SEM image in micro-technology.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{\textbf{Languages}{: Python, C\#, C++, Matlab, Markdown, Latex}}
   \item{\textbf{Framework}{: TensorFlow, PyTorch, Docker, Github}
   \item{\textbf{Technologies}{: Amazon Web Service, Apache Hadoop, Apache Spark}
 \resumeSubHeadingListEnd

 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
